PWNCAT2

### 2012-01-28 pwncatalog/PWNCAT2/paper/sections/off_peak_phase_selection.tex
updating text

\figref{off_peak_select} shows the off peak selection for some pulsars\dots

@@

The method we developed required first representing the

>>>>

The method we developed is
\begin{itemize}
  \item First, deconstruct the pulsar phaseogram 
    using a Bayseian blocks representation of the data.
    \begin{itemize}
      \item \figref{off_peak_select} shows the off peak selection for some pulsars\dots
      \item Set the ncpPrior parameter to 5
    \end{itemize}
  \item Before beinning the data, first rotate the maximum phase range to 0
    so that the off-peak region will not overlap the phase edge.
  \item 
\end{itemize}
  required first representing the

@@
